SIMD-vectorized Chemical Source Term Evaluation

### 2017-02-21 paper.tex
remove #'s in affil
reorder

\author[1,*]{Nicholas Curtis}
\author[1]{Chih-Jen Sung}

\affil[1]{Department of Mechanical Engineering, University of Connecticut, Storrs, CT 06269, USA}
\affil[*]{Corresponding author: \email{nicholas.curtis@uconn.edu}}

@@

%====================================================================
\begin{abstract} % not to exceed 200 words
A code generation platform for single-instruction, multiple-data-vectorized (SIMD) chemical source term evaluation was developed and validated against Cantera for a wide range of chemical kinetic models.
Speedups of up to \SIrange{1.88}{2.42}{$\times$} were observed over a baseline single-instruction, multiple-thread (SIMT) parallelized code.
Additionally, use of a row-major data layout was found to increase both the SIMD and SIMT performance by up to \SIrange{1.96}{2.38}{$\times$} over a column-major data layout.
Larger vector widths were found to produce speedups up to \SI{1.8}{$\times$} for smaller models, but had similar performance to smaller vector widths as the model size increased.
Finally, the parallel scaling efficiency was found to be slightly better for larger models, and future extensions of this work were discussed.
\end{abstract}

>>>>

\author[*]{Nicholas Curtis}
\author[ ]{Chih-Jen Sung}

\affil[ ]{Department of Mechanical Engineering, University of Connecticut, Storrs, CT 06269, USA}
\affil[*]{Corresponding author: \email{nicholas.curtis@uconn.edu}}

@@

%====================================================================
\begin{abstract} % not to exceed 200 words
A code generation platform for single-instruction, multiple-data (SIMD) vectorized chemical source term evaluation was developed and validated against Cantera for a wide range of chemical kinetic models.
Speedups of up to \SIrange{1.88}{2.42}{$\times$} were observed over a baseline single-instruction, multiple-thread (SIMT) parallelized code.
Additionally, use of a row-major data layout was found to increase both the SIMD and SIMT performance by up to \SIrange{1.96}{2.38}{$\times$} over a column-major data layout.
Larger vector widths were found to produce speedups up to \SI{1.8}{$\times$} for smaller models, but had similar performance to smaller vector widths as the model size increased.
Finally, the parallel scaling efficiency was found to be slightly better for larger models, and future extensions of this work were discussed.
\end{abstract}
